The Anthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-04-14 paper.tex
Use aurl.

% add. options: [seceqn,secthm,crcready]
\documentclass[sw]{iosart2x}
\usepackage{todonotes}
\usepackage{cleveref}
\usepackage{csquotes}
%\usepackage{dcolumn}

%%%%%%%%%%% Put your definitions here
\newcommand{\aw}{AnthroWorks3D}

@@

The \aw{} software (\cref{sec:aw}) is designed according to the three-ontology method~\citep{threeontologymethod}. 
This method is based on the interaction of a task ontology, a domain ontology and a top-level ontology. 
In our case, the ANNO-core plays the role of a task ontology and serves as the conceptual model of the software. 
One of the advantages of the three-ontology method is that the software only needs to implement the access to entities (classes, properties) 
of the task ontology (ANNO-core), whereas the entities of the corresponding domain ontology (ANNO-domain) are processed dynamically. 
The \aw{} uses the ANNO-core as an interface to access the ANNO-domain entities (e.g., by listing all subclasses of a specific ANNO-core class 
such as \enquote{Bone}), as described in \cref{sec:aw}.

>>>>

% add. options: [seceqn,secthm,crcready]
\documentclass[sw]{iosart2x}
\usepackage{todonotes}
\usepackage{cleveref}
\usepackage{csquotes}
\usepackage{aurl}
%\usepackage{dcolumn}

%%%%%%%%%%% Put your definitions here
\newcommand{\aw}{AnthroWorks3D}
\daurl{anno}{https://annosaxfdm.de/ontology/}

@@

The \aw{} software (\cref{sec:aw}) is designed according to the three-ontology method~\citep{threeontologymethod}. 
This method is based on the interaction of a task ontology, a domain ontology and a top-level ontology. 
In our case, the ANNO-core plays the role of a task ontology and serves as the conceptual model of the software. 
One of the advantages of the three-ontology method is that the software only needs to implement the access to entities (classes, properties) 
of the task ontology (ANNO-core), whereas the entities of the corresponding domain ontology (ANNO-domain) are processed dynamically. 
The \aw{} uses the ANNO-core as an interface to access the ANNO-domain entities, e.g. by listing all subclasses of a specific ANNO-core class, such as \aurl{anno}{Bone}, as described in \cref{sec:aw}.
